Convergence Studies of Mass Transport in Disks with Gravitational Instabilities. \\ I. The Constant Cooling Time Case

### 2011-11-30 Paper_1_submisson2.tex
Paper more or less accepted, first cut at final changes offered by referee.
	modified:   Paper_1.tex
	new file:   Paper_1_submisson2.tex
	modified:   Response_to_Referee1.txt
	modified:   general.bib

\bibliographystyle{apj}
\bibliography{general}

>>>>

\begin{thebibliography}{66}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

\bibitem[{{Balbus} \& {Papaloizou}(1999)}]{balbus1999}
{Balbus}, S.~A. \& {Papaloizou}, J.~C.~B. 1999, ApJ, 521, 650

\bibitem[{{Boley}(2009)}]{boley2009}
{Boley}, A.~C. 2009, ApJL, 695, L53

\bibitem[{{Boley} \& {Durisen}(2008)}]{boley2008}
{Boley}, A.~C. \& {Durisen}, R.~H. 2008, ApJ, 685, 1193

\bibitem[{{Boley} {et~al.}(2007{\natexlab{a}}){Boley}, {Durisen}, {Nordlund},
  \& {Lord}}]{boley2007b}
{Boley}, A.~C., {Durisen}, R.~H., {Nordlund}, {\AA}., \& {Lord}, J.
  2007{\natexlab{a}}, ApJ, 665, 1254

\bibitem[{{Boley} {et~al.}(2007{\natexlab{b}}){Boley}, {Hartquist}, {Durisen},
  \& {Michael}}]{boley2007a}
{Boley}, A.~C., {Hartquist}, T.~W., {Durisen}, R.~H., \& {Michael}, S.
  2007{\natexlab{b}}, ApJL, 656, L89

\bibitem[{{Boley} {et~al.}(2006){Boley}, {Mej{\'{\i}}a}, {Durisen}, {Cai},
  {Pickett}, \& {D'Alessio}}]{boley2006}
{Boley}, A.~C., {Mej{\'{\i}}a}, A.~C., {Durisen}, R.~H., {Cai}, K., {Pickett},
  M.~K., \& {D'Alessio}, P. 2006, ApJ, 651, 517

\bibitem[{{Boss}(1984)}]{boss1984}
{Boss}, A.~P. 1984, MNRAS, 209, 543

\bibitem[{{Boss}(2002)}]{boss2002}
---. 2002, ApJ, 576, 462

\bibitem[{{Boss}(2009)}]{boss2009}
---. 2009, ApJ, 694, 107

\bibitem[{{Cai} {et~al.}(2008){Cai}, {Durisen}, {Boley}, {Pickett}, \&
  {Mej{\'{\i}}a}}]{cai2008}
{Cai}, K., {Durisen}, R.~H., {Boley}, A.~C., {Pickett}, M.~K., \&
  {Mej{\'{\i}}a}, A.~C. 2008, ApJ, 673, 1138

\bibitem[{{Cai} {et~al.}(2006){Cai}, {Durisen}, {Michael}, {Boley},
  {Mej{\'{\i}}a}, {Pickett}, \& {D'Alessio}}]{cai2006}
{Cai}, K., {Durisen}, R.~H., {Michael}, S., {Boley}, A.~C., {Mej{\'{\i}}a},
  A.~C., {Pickett}, M.~K., \& {D'Alessio}, P. 2006, ApJL, 636, L149

\bibitem[{{Christodoulou}(1991)}]{christodoulou1991}
{Christodoulou}, D.~M. 1991, \apj, 372, 471

\bibitem[{{Clarke} {et~al.}(2007){Clarke}, {Harper-Clark}, \&
  {Lodato}}]{clarke2007}
{Clarke}, C.~J., {Harper-Clark}, E., \& {Lodato}, G. 2007, MNRAS, 381, 1543

\bibitem[{{Cossins} {et~al.}(2009){Cossins}, {Lodato}, \&
  {Clarke}}]{cossins2009}
{Cossins}, P., {Lodato}, G., \& {Clarke}, C.~J. 2009, \mnras, 393, 1157

\bibitem[{{Cossins} {et~al.}(2010){Cossins}, {Lodato}, \&
  {Clarke}}]{cossins2010}
---. 2010, \mnras, 401, 2587

\bibitem[{{Durisen} {et~al.}(2007){Durisen}, {Boss}, {Mayer}, {Nelson},
  {Quinn}, \& {Rice}}]{durisen2007}
{Durisen}, R.~H., {Boss}, A.~P., {Mayer}, L., {Nelson}, A.~F., {Quinn}, T., \&
  {Rice}, W.~K.~M. 2007, in Protostars and Planets V, B. Reipurth, D. Jewitt,
  and K. Keil (eds.), University of Arizona Press, Tucson, 951 pp., 2007.,
  p.607-622, ed. B.~{Reipurth}, D.~{Jewitt}, \& K.~{Keil}, 607--622

\bibitem[{{Durisen} {et~al.}(2005){Durisen}, {Cai}, {Mej{\'{\i}}a}, \&
  {Pickett}}]{durisen2005}
{Durisen}, R.~H., {Cai}, K., {Mej{\'{\i}}a}, A.~C., \& {Pickett}, M.~K. 2005,
  Icarus, 173, 417

\bibitem[{{Durisen} {et~al.}(1986){Durisen}, {Gingold}, {Tohline}, \&
  {Boss}}]{durisen1986}
{Durisen}, R.~H., {Gingold}, R.~A., {Tohline}, J.~E., \& {Boss}, A.~P. 1986,
  ApJ, 305, 281

\bibitem[{{Gammie}(2001)}]{gammie2001}
{Gammie}, C.~F. 2001, ApJ, 553, 174

\bibitem[{{Goldreich} \& {Lynden-Bell}(1965)}]{goldreich1965}
{Goldreich}, P. \& {Lynden-Bell}, D. 1965, MNRAS, 130, 125

\bibitem[{{Hachisu}(1986)}]{hachisu1986}
{Hachisu}, I. 1986, ApJS, 61, 479

\bibitem[{{Kratter} {et~al.}(2010){Kratter}, {Matzner}, {Krumholz}, \&
  {Klein}}]{kratter2010}
{Kratter}, K.~M., {Matzner}, C.~D., {Krumholz}, M.~R., \& {Klein}, R.~I. 2010,
  ApJ, 708, 1585

\bibitem[{{Larson}(1984)}]{larson1984}
{Larson}, R.~B. 1984, MNRAS, 206, 197

\bibitem[{{Laughlin} \& {Bodenheimer}(1994)}]{laughlin1994}
{Laughlin}, G. \& {Bodenheimer}, P. 1994, ApJ, 436, 335

\bibitem[{{Laughlin} {et~al.}(1997){Laughlin}, {Korchagin}, \&
  {Adams}}]{laughlin1997}
{Laughlin}, G., {Korchagin}, V., \& {Adams}, F.~C. 1997, ApJ, 477, 410

\bibitem[{{Laughlin} {et~al.}(1998){Laughlin}, {Korchagin}, \&
  {Adams}}]{laughlin1998}
---. 1998, ApJ, 504, 945

\bibitem[{{Laughlin} \& {Rozyczka}(1996)}]{laughlin1996}
{Laughlin}, G. \& {Rozyczka}, M. 1996, \apj, 456, 279

\bibitem[{{Lin}(1981)}]{lin1981}
{Lin}, D.~N.~C. 1981, ApJ, 246, 972

\bibitem[{{Lin} \& {Pringle}(1987)}]{lin1987}
{Lin}, D.~N.~C. \& {Pringle}, J.~E. 1987, \mnras, 225, 607

\bibitem[{{Lin} \& {Pringle}(1990)}]{lin1990}
---. 1990, ApJ, 358, 515

\bibitem[{{Lodato} \& {Rice}(2004)}]{lodato2004}
{Lodato}, G. \& {Rice}, W.~K.~M. 2004, MNRAS, 351, 630

\bibitem[{{Lodato} \& {Rice}(2005)}]{lodato2005}
---. 2005, MNRAS, 358, 1489

\bibitem[{{Lynden-Bell} \& {Kalnajs}(1972)}]{lyndenbell1972}
{Lynden-Bell}, D. \& {Kalnajs}, A.~J. 1972, MNRAS, 157, 1

\bibitem[{{Mayer} {et~al.}(2002){Mayer}, {Quinn}, {Wadsley}, \&
  {Stadel}}]{mayer2002}
{Mayer}, L., {Quinn}, T., {Wadsley}, J., \& {Stadel}, J. 2002, Science, 298,
  1756

\bibitem[{{Mej{\'{\i}}a}(2004)}]{mejiaphd2004}
{Mej{\'{\i}}a}, A.~C. 2004, PhD thesis, Indiana University

\bibitem[{{Mej{\'{\i}}a} {et~al.}(2005){Mej{\'{\i}}a}, {Durisen}, {Pickett}, \&
  {Cai}}]{mejia2005}
{Mej{\'{\i}}a}, A.~C., {Durisen}, R.~H., {Pickett}, M.~K., \& {Cai}, K. 2005,
  ApJ, 619, 1098

\bibitem[{{Meru} \& {Bate}(2011{\natexlab{a}})}]{meru2011a}
{Meru}, F. \& {Bate}, M.~R. 2011{\natexlab{a}}, MNRAS, 411, L1

\bibitem[{{Meru} \& {Bate}(2011{\natexlab{b}})}]{meru2011b}
---. 2011{\natexlab{b}}, MNRAS, 410, 559

\bibitem[{{Michael} \& {Durisen}(2010)}]{michael2010}
{Michael}, S. \& {Durisen}, R.~H. 2010, MNRAS, 406, 279

\bibitem[{{Nelson} {et~al.}(1998){Nelson}, {Benz}, {Adams}, \&
  {Arnett}}]{nelson1998}
{Nelson}, A.~F., {Benz}, W., {Adams}, F.~C., \& {Arnett}, D. 1998, ApJ, 502,
  342

\bibitem[{{Nelson} {et~al.}(2000){Nelson}, {Benz}, \&
  {Ruzmaikina}}]{nelson2000a}
{Nelson}, A.~F., {Benz}, W., \& {Ruzmaikina}, T.~V. 2000, ApJ, 529, 357

\bibitem[{{Norman} \& {Winkler}(1986)}]{norman1986}
{Norman}, M.~L. \& {Winkler}, K.-H.~A. 1986, in NATO Advanced Research Workshop
  on Astrophysical Radiation Hydrodynamics,, ed. K.-H.~A. {Winkler} \& M.~L.
  {Norman} (D. Reidel Publishing Co., Boston, MA), 187

\bibitem[{{Paczynski}(1978)}]{paczynski1978}
{Paczynski}, B. 1978, \actaa, 28, 91

\bibitem[{{Papaloizou} \& {Savonije}(1991)}]{papaloizou1991}
{Papaloizou}, J.~C. \& {Savonije}, G.~J. 1991, MNRAS, 248, 353

\bibitem[{{Pickett} {et~al.}(1998){Pickett}, {Cassen}, {Durisen}, \&
  {Link}}]{pickett1998}
{Pickett}, B.~K., {Cassen}, P., {Durisen}, R.~H., \& {Link}, R. 1998, ApJ, 504,
  468

\bibitem[{{Pickett} {et~al.}(2000){Pickett}, {Cassen}, {Durisen}, \&
  {Link}}]{pickett2000}
---. 2000, ApJ, 529, 1034

\bibitem[{{Pickett} {et~al.}(1996){Pickett}, {Durisen}, \&
  {Davis}}]{pickett1996}
{Pickett}, B.~K., {Durisen}, R.~H., \& {Davis}, G.~A. 1996, ApJ, 458, 714

\bibitem[{{Pickett} {et~al.}(2003){Pickett}, {Mej{\'{\i}}a}, {Durisen},
  {Cassen}, {Berry}, \& {Link}}]{pickett2003}
{Pickett}, B.~K., {Mej{\'{\i}}a}, A.~C., {Durisen}, R.~H., {Cassen}, P.~M.,
  {Berry}, D.~K., \& {Link}, R.~P. 2003, ApJ, 590, 1060

\bibitem[{Press {et~al.}(1992)Press, Teukolsky, Vetterling, \&
  Flannery}]{press1992}
Press, W., Teukolsky, S., Vetterling, W., \& Flannery, B. 1992, {Numerical
  Recipes in C}, 2nd edn. (Cambridge, UK: Cambridge University Press)

\bibitem[{{Pringle}(1981)}]{pringle1981}
{Pringle}, J.~E. 1981, \araa, 19, 137

\bibitem[{{Rice} {et~al.}(2003){Rice}, {Armitage}, {Bate}, \&
  {Bonnell}}]{rice2003b}
{Rice}, W.~K.~M., {Armitage}, P.~J., {Bate}, M.~R., \& {Bonnell}, I.~A. 2003,
  MNRAS, 339, 1025

\bibitem[{{Rice} {et~al.}(2005){Rice}, {Lodato}, \& {Armitage}}]{rice2005}
{Rice}, W.~K.~M., {Lodato}, G., \& {Armitage}, P.~J. 2005, MNRAS, 364, L56

\bibitem[{{Shakura} \& {Sunyaev}(1973)}]{shakura1973}
{Shakura}, N.~I. \& {Sunyaev}, R.~A. 1973, A\&A, 24, 337

\bibitem[{Shannon(1984)}]{shannon1984}
Shannon, C. 1984, Proceedings of the IEEE, 72, 1192

\bibitem[{{Shu} {et~al.}(1990){Shu}, {Tremaine}, {Adams}, \& {Ruden}}]{shu1990}
{Shu}, F.~H., {Tremaine}, S., {Adams}, F.~C., \& {Ruden}, S.~P. 1990, ApJ, 358,
  495

\bibitem[{{Stamatellos} \& {Whitworth}(2008)}]{stamatellos2008}
{Stamatellos}, D. \& {Whitworth}, A.~P. 2008, A\&A, 480, 879

\bibitem[{{Tomley} {et~al.}(1991){Tomley}, {Cassen}, \&
  {Steiman-Cameron}}]{tomley1991}
{Tomley}, L., {Cassen}, P., \& {Steiman-Cameron}, T. 1991, ApJ, 382, 530

\bibitem[{{Tomley} {et~al.}(1994){Tomley}, {Steiman-Cameron}, \&
  {Cassen}}]{tomley1994}
{Tomley}, L., {Steiman-Cameron}, T.~Y., \& {Cassen}, P. 1994, ApJ, 422, 850

\bibitem[{{Toomre}(1981)}]{toomre1981}
{Toomre}, A. 1981, in Structure and Evolution of Normal Galaxies, ed.
  {S.~M.~Fall \& D.~Lynden-Bell}, 111--136

\bibitem[{{van Albada} {et~al.}(1982){van Albada}, {van Leer}, \&
  {Roberts}}]{albada1982}
{van Albada}, G.~D., {van Leer}, B., \& {Roberts}, Jr., W.~W. 1982, \aap, 108,
  76

\bibitem[{{Vorobyov}(2010)}]{vorobyov2010}
{Vorobyov}, E.~I. 2010, New Astronomy, 15, 24

\bibitem[{{Vorobyov} \& {Basu}(2005)}]{vorobyov2005}
{Vorobyov}, E.~I. \& {Basu}, S. 2005, \mnras, 360, 675

\bibitem[{{Vorobyov} \& {Basu}(2006)}]{vorobyov2006}
---. 2006, ApJ, 650, 956

\bibitem[{{Yang}(1992)}]{yangphd1992}
{Yang}, S.~X. 1992, PhD thesis, Indiana University

\bibitem[{{Yorke} \& {Bodenheimer}(1999)}]{yorke1999}
{Yorke}, H.~W. \& {Bodenheimer}, P. 1999, ApJ, 525, 330

\bibitem[{{Yorke} {et~al.}(1993){Yorke}, {Bodenheimer}, \&
  {Laughlin}}]{yorke1993}
{Yorke}, H.~W., {Bodenheimer}, P., \& {Laughlin}, G. 1993, ApJ, 411, 274

\end{thebibliography}
